What Can Stack Traces Tell us about the Use of Exceptions in Java?

### 2014-05-07 android-stacks.tex
smal inprovements.

>>>>

We could also observe that in 205 stacks found in Android repository the exception was wrapped 
more then once. Figure ~\ref{sizewrapbhists}  illustrates the number of wrappings per stack, both
 in Java and Android studied repositories. One interesting wrapping found in ones Android repo was the 
following: Runtime-Checked-Runtime-Checked-Runtime-Checked-Runtime.
